Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-23 ms.tex
first pass at molecular emission section

@@

@@

>>>>

The following subsections detail the processing steps we have applied to 
isolate Galactic dust emission in the \PLANCK~maps in preparation for SED
fitting.

@@

We first addressed the CMB anisotropies before performing any of the 
interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
The CMB anisotropies are effectively imperceptible upon visual inspection 
of \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
are prominent at 100-353 GHz relative to the Galactic emission
we wish to characterize, especially at high latitudes.

% mention hybrid 2013/2015 release SMICA model to account for more aggressive
% inpainting ...
To remove the CMB anisotropies, we have subtracted the Spectral Matching 
Independent Component Analysis \citep[SMICA,][]{smica} model from each of the 
\PLANCK~maps, applying appropriate unit conversions for the 545 and 857 GHz 
maps with native units of MJy/sr. Low-order corrections, particularly our 
removal of  Solar dipole residuals, are discussed in $\S$\ref{sec:zp}.

@@

The \cite{planckdust} modeling did not attempt to correct for Galactic CO 
emission, due to the fact that CO emission is only important relative to
dust emission over a small region of the sky, predominantly in the Galactic 
plane and nearby molecular clouds. \cite{meisner15} attempted a CO correction 
based on the \cite{planckco} full-sky CO map. However, we have judged that the 
CO map becomes unreliable in the very highest-signal regions of molecular
clouds, and have therefore decided to adopt the \cite{planckdust} strategy
of making no CO correction. Because of this decision, we exclude 
CO-contaminated regions of the sky from all downstream analyses which are 
sensitive to the dust SED shape at low frequencies which are affected by CO 
line emission.
